Monte Carlo and bootstrap for ALL parameters

### 2024-08-12 All_param.Rmd
Work to do on EST with MC_boot

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
EST_nb <- c()
EST_vol <- c()
EST_ratio <- c()
for (elt in res2$Estimations) {
  if ("data.frame" %in% class(elt)){ # we target bootstrap samples made from each MC iteration
    EST_nb <- append(EST_nb, mean(elt$est_nb))
    EST_vol <- append(EST_vol, mean(elt$est_vol))
    EST_ratio <- append(EST_ratio, mean(elt$est_ratio))
  }
}
```

@@

```{r}
diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(res1$Variances[1], mean(VAR_nb)), "%", "\n - for the volume of trees: ", diff_percent(res1$Variances[2], mean(VAR_vol)), "%\n - for the ratio volume / number of trees: ", diff_percent(res1$Variances[3], mean(VAR_ratio)), "%", sep = "")

>>>>

```{r}
# We want all the variances obtained for each parameter of interest, 
# to find the mean for each of these series
EST_nb <- c()
EST_vol <- c()
EST_ratio <- c()
for (elt in res2$Estimations) {
  if (grepl("boot", names(elt)) ){ # we target bootstrap samples made from each MC iteration
    EST_nb <- append(EST_nb, mean(elt$est_nb))
    EST_vol <- append(EST_vol, mean(elt$est_vol))
    EST_ratio <- append(EST_ratio, mean(elt$est_ratio))
  }
}
```

@@

```{r}
diff_percent <- function(x,y){100*(max(res1$Variances[x],mean(y))-min(res1$Variances[x],mean(y)))/min(res1$Variances[x],mean(y))}
cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1, VAR_nb), "%", "\n - for the volume of trees: ", diff_percent(2, VAR_vol), "%\n - for the ratio volume / number of trees: ", diff_percent(3, VAR_ratio), "%", sep = "")
